Using an SMT engine to generate Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-18 2017-Xudong-SMT/ActaInformatica.tex
v2-2, new version

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-2}
  \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP})}
  \label{fig:FailureTimer:pNet}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{XFIG/TimerOADetailed}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{fig:ArchFailure:OA}
\end{figure}

Figure \ref{fig:ArchFailure:OA} shows the open automaton built by our
algorithm. For reasons of readability, we did not show the full
details of the open transitions on this figure. Below we list the
first 3 of them (full details available in \ref{TimerRR}). 
This automaton has 12 transitions, including those encoding various
possible firing of some interactions (e.g. OT 2 and 3 for
{\PortFail}). It looks like the rough behaviour is
reasonable, although a detailed study shows that the property stated
above does not hold, because of the
{\PortFail} loops on states $11$ and $12$. This is because we did not
use the maximal progress assumption here. If we do, we get the
corrected behaviour in Figure \ref{fig:ArchFailure:OA-MaxProgress}, in
which $OT_7$ has disappeared, and $OT_2$ and 
$OT_{10}$ have been restricted to $b0=\false$.

\bigskip
\noindent
$  OT_1  = \openrule
{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
{\ostate{00} \OTarrow{init} \ostate{11}}
$

\medskip    
\noindent
$  OT_2  = \openrule
{\{B\mapsto fail(b0)\},\\
  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
  \{z:=z1\} }
{\ostate{11} \OTarrow{fail} \ostate{11}}
$
\medskip

\noindent
  $  OT_3  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
    \{z:=z1\} }
  {\ostate{11} \OTarrow{fail} \ostate{12}}
  $
  \medskip

  \begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{XFIG/TimerOAMaxProgress}
  \caption{The open Automaton of the Failure Monitor Architecture,
    with Maximal Progress}
  \label{fig:ArchFailure:OA-MaxProgress}
  \end{figure}

  \TODO{Eric: Explain}
\begin{itemize}
\item $OT_2$ and $OT_{10}$ have changed because $b0=true$ is no longer possible
\item $OT_7$ has disappeared because it is now unsat.
\end{itemize}

@@

                (with 2 client holes)&
                2496 ms 				&
                844 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer    			&
                12/235 OTs           &
                12/180 OTs
                \\\specialrule{0em}{1pt}{1pt}

                (no Max Progress)&
                1253 UNSAT           &
                812 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                1253 ms 				&
                812 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer X 2    			&
                37/3136 OTs           &
                37/2416 OTs
                \\\specialrule{0em}{1pt}{1pt}

		&
                8923 ms 				&
                6798 ms

@@

        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 60\% gain depending on the examples.

>>>>

In the conception of the Nano satellite Software \cite[], the Failure
Timer architecture was used to control several processes
communicating on the common bus. Timeout signals (``$ask$''), resets,
and the passing of time ($tick$) were synchronised in the global
system.

In Figure~\ref{schema:ArchFailure:BIP:Double} we show the combination
of two FailureTimer architectures, with their respective controlled
processes.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-DoubleArchFailureTimer-v2-2}
  \caption{The BIP specification of the Failure Monitor architecture}
  \label{schema:ArchFailure:BIP:Double}
\end{figure}

%% \begin{figure}[t]
%%   \centering
%%   \includegraphics[width=0.9\columnwidth]{ActaXFIG/DoubleFailureTimerPNET-v2-2}
%%   \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP})}
%%   \label{fig:FailureTimer:pNet}
%% \end{figure}

%% \begin{figure}[t]
%%   \centering
%%   \includegraphics[width=0.9\columnwidth]{XFIG/DoubleTimerOA-v2-2}
%%   \caption{The open Automaton of the Failure Monitor Architecture}
%%   \label{fig:ArchFailure:OA}
%% \end{figure}

@@

                (with 2 client holes)&
                2496 ms 				&
                844 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer    			&
                12/364 OTs           &
                12/167 OTs
                \\\specialrule{0em}{1pt}{1pt}

  		&
                1080 ms 				&
                563 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer X 2    			&
                25/8964 OTs           &
                25/1255 OTs
                \\\specialrule{0em}{1pt}{1pt}

		&
                18088 ms 				&
                3266 ms

@@

        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 80\% gain depending on the examples.
